Solving the independent set problem by generic programming tensor networks \thanks{\funding{...}}

### 2021-09-08 paper/paper.tex
acknowledge

\section*{Acknowledgments}
We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
their questions are the driving force of this project.
Thank Chris Elord for helping us writting the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
\blue{funding information}

>>>>

\section*{Acknowledgments}
We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network, his code plays a crucial role in our code base.
We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
their questions are the driving force of this project.
Thank Chris Elord for helping us writting the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
\blue{funding information}
